### 2015-09-14 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
Delco_2014: updated hose test script to produce code for specific LaTeX tables, edited report
remove pdf, update tex file and add ignore file

@@

\headerC{
\flushright{
Daniel Madrzykowski \\
Craig G. Weinschenk \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

\flushright{\today \\
}

@@

\flushright{
\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
}

@@

@@

>>>>

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

@@

\headerC{
{
\flushright{
Joseph Willi \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\

\vspace*{2\baselineskip}

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\flushright{

\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
}
}
}

\newpage
\hspace{5in}
\newpage

\pagenumbering{roman}

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerC{
\flushright{
Joseph Willi \\
Daniel Madrzykowski \\
Craig G. Weinschenk \\
{\em Fire Research Division \\
Engineering Laboratory} \\

\vspace*{2\baselineskip}

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

\vspace*{2\baselineskip}
September 2015}}

\flushright{\includegraphics[width=1in]{../../../../../Bibliography/doc} }

@@

\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
document in order to describe an experimental procedure or concept adequately. \\
Such identification is not intended to imply recommendation or endorsement by the \\
National Institute of Standards and Technology, nor is it intended to imply that the \\
entities, materials, or equipment are necessarily the best available for the purpose. \\
}

\vspace{3in}

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2015) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

\vspace{0.2in}

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
\endgroup

\hspace{1in}

@@

\begin{table}[!ht]
\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and pattern combinations during Tests 18 and 19}
\begin{tabular}{lcccc}
\toprule
 & \multicolumn{4}{c}{\underline{Test 18}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
\\ \midrule
 & \multicolumn{4}{c}{\underline{Test 19}}
\\
\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
\\ \midrule
\textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
\\ \multicolumn{5}{c}{} \\
\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
\\ \bottomrule
\end{tabular}
\label{table:west_hand_A10_avgs}
\end{table}
